Paper 2: Vitamin D

### 2017-11-06 doc/vitaminD.Rmd
formatted graph outputs to match with slides colour theme

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

@@

dsBase %>% 
  scatter_plot("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

>>>>

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot_slides("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

@@

dsBase %>% 
  scatter_plot_slides("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")
